\large Neural, Tree, and Symbolic Optimization of Cosmological Particle-Mesh Simulation \vspace{0.3em}

### 2023-08-09 docs/papers/sto/so.tex
FIXUP draft: a few sentences

Given two snapshots at $a_i$ and $a_{i+1}$, we get the particle displacements
in between at $a$ using interpolation with the cubic Hermite spline,
\begin{align}
  \vx(a) =\ &h_{00}(\alpha)\vx_i + h_{10}(\alpha)(a_{i+1} - a_i)\vv_i + \nonumber\\
           &h_{01}(\alpha)\vx_{i+1} + h_{11}(\alpha)(a_{i+1} - a_i)\vv_{i+1},
\end{align}
where $\alpha := (a - a_i)/(a_{i+1} - a_i)$ and the Hermite basis functions read
\begin{align}
  h_{00}(\alpha) &= 2\alpha^3 - 3\alpha^2 + 1, \nonumber\\
  h_{10}(\alpha) &= \alpha^3 - 2\alpha^2 + \alpha, \nonumber\\
  h_{01}(\alpha) &= -2\alpha^3 + 3\alpha^2, \nonumber\\
  h_{11}(\alpha) &= \alpha^3 - \alpha^2.
\end{align}
The particle velocity is then given by the derivative $\d\vx / \d a$.

@@

Hyperparameters:
\YZ{
\begin{itemize}
  \item Model: number of hidden layers and nodes of f and g nets
  \item Optimization: learning rate scheduler, weight decay and dropout rate etc
  \item Loss: fields to include and loss function forms
\end{itemize}
}

>>>>

Given two snapshots at $a_i$ and $a_{i+1}$, we get the particle displacements
in between at $a$ using interpolation with the cubic Hermite spline,
\begin{align}
  \vx(a) =\ &h_{00}(\alpha)\vx_i + h_{10}(\alpha)(a_{i+1} - a_i)\vv_i + \nonumber\\
           &h_{01}(\alpha)\vx_{i+1} + h_{11}(\alpha)(a_{i+1} - a_i)\vv_{i+1},
\end{align}
where $\alpha := (a - a_i)/(a_{i+1} - a_i)$ and the Hermite basis functions read
\begin{align}
  h_{00}(\alpha) &= 2\alpha^3 - 3\alpha^2 + 1, \nonumber\\
  h_{10}(\alpha) &= \alpha^3 - 2\alpha^2 + \alpha, \nonumber\\
  h_{01}(\alpha) &= -2\alpha^3 + 3\alpha^2, \nonumber\\
  h_{11}(\alpha) &= \alpha^3 - \alpha^2.
\end{align}
The particle velocity is then given by the derivative $\d\vx / \d a$.
\YZ{Notice that the interpolation is a linear combination of the particles at
two consecutive time steps, which therefore can be done in either two steps or
just one step by carrying the particles from the previous time step.
We find the two-steps scheme more convenient for the backward evolution of the
adjoint variables.}

@@

Hyperparameters:
\YZ{
\begin{itemize}
  \item Model: number of hidden layers and nodes of f and g nets, activation function
  \item Optimization: learning rate scheduler, momentum, weight decay and dropout rate etc
  \item Loss: fields to include and loss function forms
\end{itemize}
}
